### 2022-05-23 chapters/literature/draft_citations.tex
refactoring : structure

\section{testing}

@@

% TODO : add a triangle to classify all those tools

@@

>>>>

\section{benchmarking}

@@

@@

\section{Conclusion}
As we have seen in the state of the art, many methodes have been proposed to reduce the energy footprint of the the ICT,which they can be applied in deffirent parts of the lifecycle of the program, from consumption to the execution. Furthermore, the execution phase took attention of many researchers because it's the part where the most energy is consumed. This thesis will focus on that aspect as well. However, unlike the most work that have been done on the hardware aspect, we will target the software impact on this energy, starting from the choice of the programming language up to how to tune some features of a frameworks in order to make the software consumes less energy.To do so we use the emprical apporach due to it's concinstency for the moment.Unlike the perfromance which essentialy related to the complexity of the algorithm, the energy consumption is more impacted by the hardware.
Therefore, to optimize the enrgy consumption we choose a spiral methode. based on 3 phases:
\begin{enumerate}
    \item execute the code
    \item measure the program
    \item infere the guidelines
\end{enumerate}

\begin{figure}[!hbt]
    \center{\includegraphics[scale=0.3]{images/greenbenchmarkcycle}}
    \caption{the spiral methode of energy optimization }\label{fig:spirals}
\end{figure}
the aim of this work is to present a set of guidelines to create a benchmarking system to to measure the energy consumption of different programs.
After that, we will use this system to compare the energy consumption of different programming languages. We will extend the work of \citeauthor{pereira2017energy} to a closer distance to production environment by comparing a set of usecases. starting by GRPC framework, and a set of Web Framewroks. Finally we will discuss the impact of the execution environment on the energy consumption of two of the most famous programming languages JAVA and Python. and present how can tunning the Virtual Machine can reduce the energy consumption.
